Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-21 revision-1/hyper.tex
checkpoint

\begin{definition}
  We say that a protocol $\prog$ with $\iov(\prog) = (S,M)$ satisfies \emph{active confidentiality} iff the following conditions hold
  for all adversaries $\adversary$:
  \begin{enumerate}
  \item $\ \,\forall \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(\{ \outv \}|\store)) =
    \support(\progtt(\prog,\adversary)(\{ \outv \}|\store))$
  \item $\begin{array}[t]{l}\forall \store_1, \store_2 \in \mems(S_H), \store \in \mems(\cinputs)\ . \\
    \quad
    \condd{\progtt(\prog,\adversary)}{\{ \outv \}}{\store_1 \cup \store} =
    \condd{\progtt(\prog,\adversary)}{\{ \outv \}}{\store_2 \cup \store} \\
    \qquad \implies\\
    \quad
    \condd{\progtt(\prog,\adversary)}{\houtputs}{\store_1 \cup \store} =
    \condd{\progtt(\prog,\adversary)}{\houtputs}{\store_2 \cup \store}\end{array}$
  \end{enumerate}
\end{definition}

@@

\begin{definition}
  A protocol $\prog$ with $\iov(\prog) = (S,M,O)$ is \emph{malicious correct} iff:
  $$
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) =
    \support(\progtt(\prog,\adversary)(O_H|\store))
  $$
\end{definition}

>>>>

\begin{definition}[Malicious Correctness]
  A protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is \emph{malicious correct} iff
  $
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) =
    \support(\progtt(\prog,\adversary)(O_H|\store))
  $.
\end{definition}

\begin{definition}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ satisfies
  \emph{active confidentiality} iff
  it is malicious correct, and for all adversaries $\adversary$:
  %\begin{enumerate}
  %\item $\ \,\forall \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(\{ \outv \}|\store)) =
    %\support(\progtt(\prog,\adversary)(\{ \outv \}|\store))$
    %\item
    $$\begin{array}[t]{l}\forall \store_1, \store_2 \in \mems(S_H), \store \in \mems(\cinputs)\ . \\
    \quad
    \condd{\progtt(\prog,\adversary)}{O_H}{\store_1 \cup \store} =
    \condd{\progtt(\prog,\adversary)}{O_H}{\store_2 \cup \store} 
    %\qquad
    \implies
    %\quad
    \condd{\progtt(\prog,\adversary)}{\houtputs}{\store_1 \cup \store} =
    \condd{\progtt(\prog,\adversary)}{\houtputs}{\store_2 \cup \store}
    \end{array}$$
  %\end{enumerate}
\end{definition}

@@
